---
title: "TTD studies in real-world catchments from post-2006 methods"
knit: (function(inputFile, encoding) { 
      out_dir <- file.path("..");
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'README.md')) })
output: 
  github_document
always_allow_html: yes  
---

```{r message=FALSE, warning=FALSE, include=FALSE}

# the working directory needs to be the 'scripts' folder

# load all packages 
library(readr)
library(stringr)
library(dplyr)
library(tidyr)
library(stringr)
library(glue)
library(tibble)
library(knitr)
library(kableExtra)

# process all the data through script "data_import.R" and import 3 tibbles:
  # T, with all the data on the studies and their sites (not really needed)
  # Tdisplay, which is the same as T but with html entries that are good for html display
  # Tsites, with all the info on the study sites
source(file.path("data_import.R"))
```

This repository explores a list of scientific studies on water transit time distributions (TTD) in real-world systems. The list currently includes `r nrow(Tdisplay)` applications to `r T %>% distinct(site) %>% count()` distinct sites, from `r length(unique(Tdisplay$study))` papers published between `r min(Tdisplay$year)` and `r max(Tdisplay$year)`. A study is included if it is based on tracer data and if it makes use of post-2006 approaches to estimate TTDs or TTD metrics.


## Display the data

The list can be displayed through:

- A **table with all the studies** ([below](#table-with-all-the-studies) or <a href="https://pbenettin.github.io/TTDstudies/html_files/table_studies.html" target="_blank">interactive</a>)

- A **table with all the study sites** ([below](#table-with-the-study-sites) or <a href="https://pbenettin.github.io/TTDstudies/html_files/table_sites.html" target="_blank">interactive</a>)

- A **map of the sites** (<a href="https://pbenettin.github.io/TTDstudies/html_files/map_sites.html" target="_blank">interactive</a>)


Some additional basic analyses can be run through the R Markdown script `data_analysis.Rmd`.


## How to contribute

Please feel free to suggest additional studies that may have been left out by mistake. You can directly send a table entry formatted as in the tables `data/table_papers.csv` and `data/sites_location_classified.csv`.



## Table with all the studies

```{r echo=FALSE, message=FALSE, warning=FALSE}
# display as a table with kable (no html tables supported in .md files)
Tdisplay %>%
  arrange(desc(year)) %>%
  dplyr::select(study, year, site, system, tracer,`TTD approach`,`estimated age metric`) %>% #select just some variables for display
  kbl(escape=FALSE) %>%
  kable_styling()
```


## Table with the study sites

```{r echo=FALSE, message=FALSE, warning=FALSE}
# display as a table with kable (no html tables supported in .md files)
Tsites %>%
  dplyr::select(-climate_main,-climate_description, -n_studies) %>%
  kbl(col.names = c('site','system','size km2','country','latitude','longitude','climate','studies'),
      escape=FALSE) %>%
  kable_styling()
```




